Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-21 article.tex
explain better the graph
math caption to actual filtering stpe

\begin{figure}
\centering
\subfigure[Original]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass $f_1(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass $g(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Thresholding $h(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Weights $w(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
\caption{Signal processing process for extracting peaks from the raw fluorescence data.
         \textcolor{red}{AJ: The bottom axe is hidden on some figures.}}
\label{fig:filtered-signal}
\end{figure}

@@

At this step, the processed signal only contains clean spikes. However, when a
large part of the network is firing, detecting pairwise neuron interactions is a
difficult task. Futhermore, it is even possible that neurons fire because of global high activity, without actual cause (see \cite{stetter2012model}).
% \textcolor{red}{G: say that neurons may fire because of global
% high activity, without any actual cause -- see generator.}
Accordingly, in order to reduce false interaction detection,
peak intensities at time $t$ are regularized by the global activity of all
neurons, thereby reducing the importance of peaks identified during global high activity periods:
\begin{align}
 w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}.
\end{align}

@@

\begin{figure}[bth]
\centering
\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         averaged partial correlation method, partial correlation used
         filter $f_1$). }
\label{fig:curves}
\end{figure}

>>>>

\begin{figure}
\centering
\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
\caption{Signal processing process for extracting peaks from the raw fluorescence data.
         \textcolor{red}{AJ: The bottom axe is hidden on some figures.}}
\label{fig:filtered-signal}
\end{figure}

@@

At this step, the processed signal only contains clean spikes. However, when a
large part of the network is firing, detecting pairwise neuron interactions is a
difficult task. Furthermore, it is even possible that neurons spike because of
a global high activity, without any actual cause (see \cite{stetter2012model}).
% \textcolor{red}{G: say that neurons may fire because of global
% high activity, without any actual cause -- see generator.}
Accordingly, in order to reduce false interaction detection,
peak intensities at time $t$ are regularized by the global activity of all
neurons, thereby reducing the importance of peaks identified during global
high activity periods:
\begin{align}
 w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}.
\end{align}

@@

\begin{figure}[bth]
\centering
\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         averaged partial correlation method, partial correlation used
         filter $f_1$). Area under the curves are given between $()$
         for the corresponding methods.}
\label{fig:curves}
\end{figure}
